### 2022-07-25 main/chapter_2ljets.tex
expand conclusion on diboson; add some todos

This assignment varies CR-VZ and on-shell other regions identically,
and since the diboson background is normalized to CR-VZ this means that
these variations have no effect in on-shell regions, and cannot move to
fit the SR-Low or SR-High-8 deficits.
Had we considered complete alternative diboson samples, we would certainly
had had some meaningful variations to apply in those regions, but I have no
way of knowing how large those variations would be.

\subsubsection{Alternative \texorpdfstring{$\ttbar$}{ttbar}}
\label{sec:2ljets_ttbar_alt}
\TODO{}

\subsection{Signals}
\label{sec:2ljets_signal_variations}

@@

\subsection{Theory}
\label{sec:2ljets_theory_variations}
\TODO{put this above alternative samples}
% extrapolation
The total theory variation is a combination of seven components, representing
\TODO{what are they?}.
A relative uncertainty due to each, $r$, is evaluated at each benchmark
point $\vec y_i$, and extrapolated elsewhere as an exponentially weighted
combination
\begin{equation}
\label{eqn:2ljets_signal_extrap}
r(\vec x) = \frac{
\sum_i r_i e^{-d(\vec x, \vec y_i)}
}{
\sum_i e^{-d(\vec x, \vec y_i)}
}
\end{equation}
in which $d(\vec x, \vec y)$ is a distance function chosen to encode some
physical understanding into the extrapolation.

>>>>

This assignment varies CR-VZ and on-shell other regions identically,
and since the diboson background is normalized to CR-VZ this means that
these variations have no effect in on-shell regions, and cannot move to
fit the SR-Low or SR-High-8 deficits.

Had we considered complete alternative diboson samples, we would certainly
have had some meaningful variations to apply in those regions, but I do not
know how large those variations should be.
This lack of a real alternative sample is particularly disappointing since
diboson is our most important background.
In hindsight, it may have been sensible to push for more resources to be
allocated to resolve this problem.

\TODO{Other theory variations; these are less important / interesting.
bullet point quickly.}
\subsubsection{Alternative \texorpdfstring{$\ttbar$}{ttbar}}
\label{sec:2ljets_ttbar_alt}
\TODO{}

\TODO{Signal theory variations}
\subsection{Signals}
\label{sec:2ljets_signal_variations}

@@

\subsection{Theory}
\label{sec:2ljets_theory_variations}
\TODO{put this above alternative samples?}
\TODO{this appears to be signal theory}
% extrapolation
The total theory variation is a combination of seven components, representing
\TODO{what are they?}.
A relative uncertainty due to each, $r$, is evaluated at each benchmark
point $\vec y_i$, and extrapolated elsewhere as an exponentially weighted
combination
\begin{equation}
\label{eqn:2ljets_signal_extrap}
r(\vec x) = \frac{
\sum_i r_i e^{-d(\vec x, \vec y_i)}
}{
\sum_i e^{-d(\vec x, \vec y_i)}
}
\end{equation}
in which $d(\vec x, \vec y)$ is a distance function chosen to encode some
physical understanding into the extrapolation.
